Kids Moisture Summary

### 2020-01-30 filter_treatment_obs_check.Rmd
SUMs cleaning and analysis

---
title: "KidsAIR: treatment filtering and missing data check"
author: "Ethan Walker"
date: "Started 21 Jan 2020, Updated 23 Jan 2020"
output: pdf_document
---

@@

# SUMs data
## 80/93 placebo homes from Winter 1 have SUMs data
## 77/88 education homes from Winter 1 have SUMs data
## 70/86 filter homes from Winter 1 have SUMs data
## All data is accounted for; missing data is truly missing from data collection issues
```{r}
sums_check <- sums_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  group_by(area, home) %>% 
  summarize(n())

>>>>

---
title: "KidsAIR: treatment filtering and missing data check"
author: "Ethan Walker"
date: "Started 21 Jan 2020, Updated 30 Jan 2020"
output: pdf_document
---

@@

# SUMs data
## 77/93 placebo homes from Winter 1 have SUMs data
## 73/88 education homes from Winter 1 have SUMs data
## 70/86 filter homes from Winter 1 have SUMs data
## All data is accounted for; missing data is truly missing from data collection issues
```{r}
sums_check <- sums_clean %>% 
  # change to correct joining data of interest
  left_join(pm_homes_placebo, by = c("area", "home", "home_winter_id")) %>% 
  filter(pm_home == "true") %>% 
  filter(winter_id == 1) %>% 
  group_by(area, home) %>% 
  summarize(n())

### 2020-01-30 moisture_data_cleaning.Rmd
data cleaning
SUMs cleaning and analysis

---
title: "KidsAIR initial moisture content data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 14 Jan 2020"
output: pdf_document
---

@@

moisture_clean <- kids_moisture %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id"))

>>>>

---
title: "KidsAIR initial moisture content data work"
author: "Ethan Walker"
date: "Started 19 Nov 2019, Updated 30 Jan 2020"
output: pdf_document
---

@@

moisture_clean <- kids_moisture %>% 
  left_join(kids_linked_ids, by = c("area", "home_winter_id")) %>% 
  replace_with_na(replace = list(moisture_ave = "NaN")) %>% 
  # lower range on instrument = 5%
  # therefore, changing values < 5 to 5
  mutate(moisture_1 = if_else(moisture_1 < 5, 5, moisture_1),
         moisture_2 = if_else(moisture_2 < 5, 5, moisture_2),
         moisture_3 = if_else(moisture_3 < 5, 5, moisture_3),
         moisture_ave = if_else(moisture_ave < 5, 5, moisture_ave))

### 2020-01-30 moisture_summary.Rmd
SUMs cleaning and analysis

---
title: "Kids Moisture Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 28 Jan 2020"
output: pdf_document
---

@@

# Summarize home data
```{r}
# Summarize numeric vars
kids_moisture <- moisture_filtered %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(moisture_ave, na.rm = TRUE), 
            "SD" = sd(moisture_ave, na.rm = TRUE),
            "min" = min(moisture_ave, na.rm = TRUE), 
            "med" = median(moisture_ave, na.rm = TRUE), 
            "max" = max(moisture_ave, na.rm = TRUE))
kable(kids_moisture, digits = 1, align = "c")

>>>>

---
title: "Kids Moisture Summary"
author: "Ethan Walker"
date: "Started 22 Nov 2019, Updated 30 Jan 2020"
output: pdf_document
---

@@

# Summarize home data
```{r}
# Summarize numeric vars
kids_moisture <- moisture_filtered_time %>%  
  group_by(area) %>% 
  summarize("Mean" = mean(moisture_ave, na.rm = TRUE), 
            "SD" = sd(moisture_ave, na.rm = TRUE),
            "min" = min(moisture_ave, na.rm = TRUE), 
            "med" = median(moisture_ave, na.rm = TRUE), 
            "max" = max(moisture_ave, na.rm = TRUE))
kable(kids_moisture, digits = 1, align = "c")
